Decoding the Amplitude-Modulated Part the DCF77 Longwave Time Signal by using the Goertzel Algorithm

### 2024-08-16 paper/main.tex
First part of the description of the DCF77 signal done

\begin{figure}[!h]
    \centering
    \resizebox{0.48\textwidth}{!}{
        \begin{tikzpicture}
            \clip (-11.5,-1) rectangle + (23,5); %Clipping: where to start, shape and size

@@

\begin{figure}[htbp]
\centerline{\includegraphics{fig1.png}}
\caption{Example of a figure caption.}
\label{fig}
\end{figure}

@@

\begin{thebibliography}{00}
\bibitem{b1} -, ``DCF77,'' 2023, Wikipedia entry. [Online]. Available: https://de.wikipedia.org/wiki/DCF77
\bibitem{b2} D. Priester and P. Hetzel and A. Bauch, ``Zeit- und Normalfrequenzverbreitung mit DCF77,'' PTB Mitteilungen, 2004, [Online]. Available: https://www.ptb.de/cms/fileadmin/internet/fachabteilungen/abteilung\_4/4.4\_zeit\_und\_frequenz/4.42/dcf77.pdf

\bibitem{b3} I. S. Jacobs and C. P. Bean, ``Fine particles, thin films and exchange anisotropy,'' in Magnetism, vol. III, G. T. Rado and H. Suhl, Eds. New York: Academic, 1963, pp. 271--350.
\bibitem{b4} K. Elissa, ``Title of paper if known,'' unpublished.
\bibitem{b5} R. Nicole, ``Title of paper with only first word capitalized,'' J. Name Stand. Abbrev., in press.
\bibitem{b6} Y. Yorozu, M. Hirano, K. Oka, and Y. Tagawa, ``Electron spectroscopy studies on magneto-optical media and plastic substrate interface,'' IEEE Transl. J. Magn. Japan, vol. 2, pp. 740--741, August 1987 [Digests 9th Annual Conf. Magnetics Japan, p. 301, 1982].
\bibitem{b7} M. Young, The Technical Writer's Handbook. Mill Valley, CA: University Science, 1989.

\bibitem{b9} S. Liu, ``Wi-Fi Energy Detection Testbed (12MTC),'' 2023, gitHub repository. [Online]. Available: https://github.com/liustone99/Wi-Fi-Energy-Detection-Testbed-12MTC
\bibitem{b10} ``Treatment episode data set: discharges (TEDS-D): concatenated, 2006 to 2009.'' U.S. Department of Health and Human Services, Substance Abuse and Mental Health Services Administration, Office of Applied Studies, August, 2013, DOI:10.3886/ICPSR30122.v2
\bibitem{b11} K. Eves and J. Valasek, ``Adaptive control for singularly perturbed systems examples,'' Code Ocean, Aug. 2023. [Online]. Available: https://codeocean.com/capsule/4989235/tree
\end{thebibliography}

>>>>

\section{The DCF77 signal}
The DCF77 station operates in the long wave area at a frequency of \SI{77.5}{\kilo\hertz}.
Its operation started with transmitting a frequency standard in 1959.
In 1973, the transmission of the current time information was added to the signal by using amplitude modulation.
To allow a reception under more challenging conditions and with a higher resolution and accuracy, the same time information is also added to the signal since 1983 by using phase-modulation \cite{b3}.
The two different parts of the signal that result out of the parallel amplitude and the phase-modulation can be used for different use-cases that are separated by the
requirements regarding the resolution, accuracy, and the reliability of the obtained time information. 
Whereas the amplitude-modulated part is mainly used for general-purpose time application with low resolution requirements, the phase-modulated part is usually used
for specialized applications that require a higher resolution, accuracy, and reliability.
Although being considered as low in comparison to what is achievable by analyzing the phase-modulated part, the usually observed accuracy uncertainity when using the
amplitude-modulated part it is still well below \SI{1}{\second}, being \SI{100}{\milli\second} \cite{b2}.
When using the phase-modulated part, a standard deviation of \SIrange{\pm 2}{\pm 22}{\micro\second} from the atomic clock to the receving device can be observed \cite{b4}.
\par
As the amplitude-modulated part allows simplistic receiver designs through its straightfoward modulation scheme, it is used in the principle presented in this paper
and a focus is put on explaining this part of the DCF77 signal.

\section{Principle of a DCF77 receiver}
\begin{figure}[!h]
    \centering
    \resizebox{0.48\textwidth}{!}{
        \begin{tikzpicture}
            \clip (-11.5,-1) rectangle + (23,5); %Clipping: where to start, shape and size

@@

\begin{figure}[htbp]
\centerline{\includegraphics{img/fig1.png}}
\caption{Example of a figure caption.}
\label{fig}
\end{figure}

@@

\begin{thebibliography}{00}
\bibitem{b1} -, ``DCF77,'' 2023, Wikipedia entry. [Online]. Available: https://de.wikipedia.org/wiki/DCF77
\bibitem{b2} D. Priester and P. Hetzel and A. Bauch, ``Zeit- und Normalfrequenzverbreitung mit DCF77,'' PTB Mitteilungen, 2004, [Online]. Available: https://www.ptb.de/cms/fileadmin/internet/fachabteilungen/abteilung\_4/4.4\_zeit\_und\_frequenz/4.42/dcf77.pdf
\bibitem{b3} D. Priester and P. Hetzel and A. Bauch, ``Zeit- und Normalfrequenzverbreitung mit DCF77: 1959-2009 und darüber hinaus,'' PTB Mitteilungen, 2009, [Online]. Available: https://www.ptb.de/cms/fileadmin/internet/fachabteilungen/abteilung\_4/4.4\_zeit\_und\_frequenz/pdf/2009\_Bauch\_PTBM\_\_DCF77.pdf
\bibitem{b4} P. Hetzel, ``Time dissemination via the LF transmitter DCF77 using a pseudo-random phase-shift keying of the carrier,'' PTB Braunschweig, 1988, [Online]. Available: https://www.ptb.de/cms/fileadmin/internet/fachabteilungen/abteilung\_4/4.4\_zeit\_und\_frequenz/pdf/5\_1988\_Hetzel\_-\_Proc\_EFTF\_88.pdf

%\bibitem{b3} I. S. Jacobs and C. P. Bean, ``Fine particles, thin films and exchange anisotropy,'' in Magnetism, vol. III, G. T. Rado and H. Suhl, Eds. New York: Academic, 1963, pp. 271--350.
%\bibitem{b4} K. Elissa, ``Title of paper if known,'' unpublished.
%\bibitem{b5} R. Nicole, ``Title of paper with only first word capitalized,'' J. Name Stand. Abbrev., in press.
%\bibitem{b6} Y. Yorozu, M. Hirano, K. Oka, and Y. Tagawa, ``Electron spectroscopy studies on magneto-optical media and plastic substrate interface,'' IEEE Transl. J. Magn. Japan, vol. 2, pp. 740--741, August 1987 [Digests 9th Annual Conf. Magnetics Japan, p. 301, 1982].
%\bibitem{b7} M. Young, The Technical Writer's Handbook. Mill Valley, CA: University Science, 1989.
%\bibitem{b9} S. Liu, ``Wi-Fi Energy Detection Testbed (12MTC),'' 2023, gitHub repository. [Online]. Available: https://github.com/liustone99/Wi-Fi-Energy-Detection-Testbed-12MTC
%\bibitem{b10} ``Treatment episode data set: discharges (TEDS-D): concatenated, 2006 to 2009.'' U.S. Department of Health and Human Services, Substance Abuse and Mental Health Services Administration, Office of Applied Studies, August, 2013, DOI:10.3886/ICPSR30122.v2
%\bibitem{b11} K. Eves and J. Valasek, ``Adaptive control for singularly perturbed systems examples,'' Code Ocean, Aug. 2023. [Online]. Available: https://codeocean.com/capsule/4989235/tree
\end{thebibliography}
